Functional Enrichment Tests: Intro and methods comparison

### 2023-06-22 DRAFT_Funct_Enrich.Rmd
annot gff fE

```{r engine='bash', eval=FALSE}

/home/shared/ncbi-blast-2.11.0+/bin/makeblastdb \
-in DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02.fasta \
-dbtype prot \
-out DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02
```

@@

```{r engine='bash', eval=FALSE}

head DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa

@@

```{bash}
/home/shared/ncbi-blast-2.11.0+/bin/blastp \
-query DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa \
-db DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02 \
-out DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab \
-evalue 1E-20 \
-num_threads 40 \
-max_target_seqs 1 \
-outfmt 6
```

>>>>

```{r engine='bash', eval=FALSE}
/home/shared/ncbi-blast-2.11.0+/bin/makeblastdb \
-in DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02.fasta \
-dbtype prot \
-out DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02
```

@@

```{r engine='bash', eval=FALSE}
head -2 DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa

@@

```
>lcl|NC_035780.1_prot_XP_022327646.1_1 [gene=LOC111126949] [db_xref=GeneID:111126949] [protein=UNC5C-like protein] [protein_id=XP_022327646.1] [location=join(30535..31557,31736..31887,31977..32565,32959..33204)] [gbkey=CDS]
MTEVCYIWASSSTTVVICGIFFIVWRCFISIKKRASPLHGSSQQVCQTCQIEGHDFGEFQLSCRRQNTNVGYDLQGRRSD

```
```{r engine='bash', eval=FALSE}
/home/shared/ncbi-blast-2.11.0+/bin/blastp \
-query DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa \
-db DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02 \
-out DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab \
-evalue 1E-20 \
-num_threads 40 \
-max_target_seqs 1 \
-outfmt 6
```

Here is what the output file looks like, and at this point we want to get the UniProt Accession number for each gene

```{r engine='bash', eval=TRUE}
head -2 DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab \
```

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_genomic.gff.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_genomic.gff.gz
```

You will notice the LOC iD is not present, but we will revisit that later with some

!tr '|' '\t' < $blastout \
> _blast-sep.tab

!awk -v OFS='\t' '{print $4, $1, $14}' < _blast-sep.tab | sort \
> _blast-sort.tab
